Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex

\subsection{Results}
\begin{table*}
\small
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.45 $\sigma$=.37, $\bar{r}$=.45 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.29, $\bar{r}$=.66 $\sigma$=.24  & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

@@

\from{klenk}{I guess we should rotate the above table. And it has been awhile since I wrote academic, so feel free to cut the boring text below}

Table~\ref{tab:overall} summarizes the results by combining each problem instance and user-defined target region. Both precision and recall for the inferred regions is .45 with a standard deviation of .37 and .38 respectively. When comparing the manually encoded regions against each target instance, we calculate a mean precision of .71 ($\sigma$=.29) and recall of .66 ($\sigma$=.24). The region defined by the room results in a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

% these are sensible results, nice

\begin{table*}
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.33 $\sigma$=.34, $\bar{r}$=.52 $\sigma$=.40 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.82 $\sigma$=.19  & $\bar{p}$=.15 $\sigma$=.09, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.45 $\sigma$=.35, $\bar{r}$=.56 $\sigma$=.40 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.62 $\sigma$=.36, $\bar{r}$=.22 $\sigma$=.21 & $\bar{p}$=.82 $\sigma$=.30, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.74 $\sigma$=.28, $\bar{r}$=.43 $\sigma$=.23 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.23 $\sigma$=.03, $\bar{r}$=.09 $\sigma$=.02 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.05 $\sigma$=.01, $\bar{r}$=.06 $\sigma$=.06 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.93 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=0 $\sigma$=0, $\bar{r}$=0 $\sigma$=0 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

Table~\ref{tab:region} separates the results by CDSR type. The mean precision for the transferred regions ranged from .74 for the back rows to 0 for the living room of the studio apartment. Comparing manually encoded against  target regions resulted in a minimum mean precision of .60. This  occurred for the front of the classroom. The whole room precision, which is directly proportionally to the size of the target region, varied from .08 for the office to .35 for the living area.

%(3 :transfer-p (0.5649091160864536d0 . 0.3824746399624735d0)  :transfer-r (0.4264200799557943d0 . 0.34846457388485863d0) :self-p   (0.8290901572528112d0 . 0.19630847005535487d0) :self-r
%  (0.6113880445364026d0 . 0.22432810023132582d0) :room-p
%  (0.20903207305733315d0 . 0.10291204447091876d0) :room-r
%  (0.9960679285191474d0 . 0.011022662977174953d0))
% (2 :transfer-p (0.4496053675639215d0 . 0.36845133415546233d0)
%  :transfer-r (0.4174204919721308d0 . 0.3697742376406773d0) :self-p
%  (0.7556540963495391d0 . 0.2672139547143468d0) :self-r
%  (0.6252647119318083d0 . 0.23778540411202373d0) :room-p
%  (0.17891943994602752d0 . 0.11273973943366206d0) :room-r
%  (0.95742701954372d0 . 0.08432884603590181d0))
% (1 :transfer-p (0.3360804531954755d0 . 0.3364697224078454d0)
%  :transfer-r (0.5074731366878895d0 . 0.4231938085019586d0) :self-p
%  (0.5493333659045643d0 . 0.33190756014975015d0) :self-r
%  (0.7596761147032691d0 . 0.25387231566349d0) :room-p
%  (0.12277614149421091d0 . 0.10953121808467986d0) :room-r
%  (0.9946881982552835d0 . 0.011992196508589958d0))

>>>>

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.47 $\sigma$=.37, $\bar{r}$=.46 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.30, $\bar{r}$=.67 $\sigma$=.25 & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

@@

To assess overall performance, Table~\ref{tab:overall} summarizes the results across all problem instances against user-defined target regions from three different users. Both precision and recall for the inferred regions is .47 and .37 with a standard deviation of .37 and .38 respectively. When comparing the manually encoded regions against each target instance, we calculate a mean precision of .71 ($\sigma$=.30) and recall of .67 ($\sigma$=.25). The region defined by the room results in a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.32 $\sigma$=.33, $\bar{r}$=.49 $\sigma$=.41 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.83 $\sigma$=.19  & $\bar{p}$=.16 $\sigma$=.10, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.44 $\sigma$=.37, $\bar{r}$=.56 $\sigma$=.41 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.76 $\sigma$=.27, $\bar{r}$=.28 $\sigma$=.21 & $\bar{p}$=.83 $\sigma$=.31, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.72 $\sigma$=.30, $\bar{r}$=.42 $\sigma$=.26 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.60 $\sigma$=.05, $\bar{r}$=.59 $\sigma$=.34 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.00 $\sigma$=.00, $\bar{r}$=.00 $\sigma$=.00 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.94 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=.40 $\sigma$=.39, $\bar{r}$=.01 $\sigma$=.01 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

\note{Klenk}{UPDATE TABLE and specific numbers in these sections.}

To identify how our approach fairs under different conditions, Table~\ref{tab:region} separates the results by CDSR type. The mean precision for the transferred regions ranged from .74 for the back rows of classrooms to 0 for the office in studio apartments. Comparing manually encoded against  target regions resulted in a minimum mean precision of .60. This occurred for the front of the classroom. The whole room precision, which is directly proportionally to the size of the target region, varied from .08 for the office to .35 for the living area.
